An Introduction to Rocker: Docker Containers for R

### 2017-07-10 manuscript.Rmd

---
title: "An Introduction to Rocker: Docker Containers for R"
author:
  - name: Carl Boettiger
    affiliation: UC Berkeley 
    address:
    - ESPM Department, University of California,
    - 130 Mulford Hall Berkeley, CA 94720-3114, USA
    email:  cboettig@berkeley.edu
  - name: Dirk Eddelbuettel
    affiliation: Debian and R Projects; Ketchum Trading
    address: 
    - Chicago, IL, USA
    email:  edd@debian.org
abstract: >
  We describe the Rocker project, which provides a widely-used suite of Docker images
  with customized R environments for particular tasks. We discuss how this suite is
  organized and how these tools can increase portability, scaling, reproducibility,
  and convenience of R users and developers.
preamble: >
   \usepackage{longtable}
   \usepackage{svg}
output: rticles::rjournal_article
---

>>>>

---
title: "An Introduction to Rocker: Docker Containers for R"
author:
  - name: Carl Boettiger
    affiliation: UC Berkeley 
    address:
    - ESPM Department, University of California,
    - 130 Mulford Hall Berkeley, CA 94720-3114, USA
    email:  cboettig@berkeley.edu
  - name: Dirk Eddelbuettel
    affiliation: Debian and R Projects; Ketchum Trading
    address: 
    - Chicago, IL, USA
    email:  edd@debian.org
abstract: >
  We describe the Rocker project, which provides a widely-used suite of Docker images
  with customized R environments for particular tasks. We discuss how this suite is
  organized and how these tools can increase portability, scaling, reproducibility,
  and convenience of R users and developers.
preamble: >
   \usepackage{longtable}
output: rticles::rjournal_article
---

<!-- Notes to Dirk: 
     Some of this material may be more appropriate for documentation elsewhere, appearing here in only abbreviated form.  
     To get started, I've just tried to err on the side of comprehensive, particularly since our documentation in places is sparse
     or dated.  Feel free to flag any areas that should be moved in part or whole to documentation.  -->
